---
title: "Hospital Admissions"
author: "AJ Clarkin"
date: "22/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r imports}

library(tidyverse)
library(here)

data <- read_csv(here("data_raw/population_demographics.csv"))


```



## Task
We want you to read in the data and answer the following questions:

- Are there any problems with the values of age and deprivation?
- What is the minimum, maximum and median age for each deprivation level?


From the data dictionary age should be in the range 0 to 105 and deprivation 1-5.

```{r task}

summary(data)

# We can look at the count of each age to see what's going on:
data %>% group_by(age) %>% summarise(n()) %>% View()


```
### Age
Has a maximum value of 150 which is incorrect. Looks like an error code - the next age is 99.


### Deprivation
There are 71 NAs but the range looks ok.


```{r groups}

# First let's get rid of the rubbish data (multiple criteria are combined with AND)
data_filtered <- data %>% 
  filter(age != 150,
         !is.na(deprivation))

data_filtered %>% summary()

data_filtered %>% group_by(deprivation) %>% 
  summarise(min_age=min(age), max_age=max(age), median_age=median(age))



```

