---
title: "Summarise Dates"
author: "AJ Clarkin"
date: "03/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r includes}

library(tidyverse)
library(lubridate)

hosp_adm <- read_csv("data_raw/hospital_admissions.csv")
pop_data <- read_csv("data_raw/population_demographics.csv")

```
## Join Datasets

From the two datasets we want to know about patients who were admitted. Therefore need all the data from hosp_adm and only the matching rows from pop_data.
Left join would do this but there is a risk of missing data in the population data. Inner join will ensure we only process full data.


```{r}


df <- inner_join(hosp_adm, pop_data, by="id")

glimpse(df)

```

## Sort out Dates

The dates are imported in dd/MM/yyyy format and need to be converted for processing.


```{r date-manuipulation}

df_proc <- df %>% 
  mutate(
    dt_adm = dmy(date_admit),
    dt_dis = dmy(date_discharge),
    diff = as.integer(dt_dis - dt_adm)
  )

head(df_proc)
  
  
```

## Grouping

```{r grouping}

df_grp <- df_proc %>% 
  group_by(deprivation, diff) %>% 
  summarise(num = n())

df_grp


```

## Visualise
No point in using a table, there's too much data

```{r}

df_grp %>% ggplot(aes(x=num)) +
  geom_histogram(bins = 10) +
  facet_wrap(~deprivation)


```

